---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# poissonreg

<!-- badges: start -->
[![R-CMD-check](https://github.com/tidymodels/poissonreg/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tidymodels/poissonreg/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/poissonreg)](https://CRAN.R-project.org/package=poissonreg)
[![Codecov test coverage](https://codecov.io/gh/tidymodels/poissonreg/branch/main/graph/badge.svg)](https://app.codecov.io/gh/tidymodels/poissonreg?branch=main)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

poissonreg enables the parsnip package to fit various types of Poisson regression models including ordinary generalized linear models, simple Bayesian models (via rstanarm), and two zero-inflated Poisson models (via pscl). 

## Installation

You can install the released version of poissonreg from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("poissonreg")
```

Install the development version from GitHub with:

``` r
require("devtools")
install_github("tidymodels/poissonreg")
```

## Available Engines

The poissonreg package provides engines for the models in the following table.

```{r, echo=FALSE, message=FALSE}
library(parsnip)

parsnip_models <- get_from_env("models") %>%
  setNames(., .) %>%
  purrr::map_dfr(get_from_env, .id = "model")

library(poissonreg)

poissonreg_models <- get_from_env("models") %>%
  setNames(., .) %>%
  purrr::map_dfr(get_from_env, .id = "model")

dplyr::anti_join(
  poissonreg_models, parsnip_models, 
  by = c("model", "engine", "mode")
) %>%
  knitr::kable()
```

## Example

A log-linear model for categorical data analysis: 

```{r example}
library(poissonreg)

# 3D contingency table from Agresti (2007): 
poisson_reg() %>% 
  set_engine("glm") %>% 
  fit(count ~ (.)^2, data = seniors)
```

## Contributing

This project is released with a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

- For questions and discussions about tidymodels packages, modeling, and machine learning, please [post on RStudio Community](https://community.rstudio.com/new-topic?category_id=15&tags=tidymodels,question).

- If you think you have encountered a bug, please [submit an issue](https://github.com/tidymodels/poissonreg/issues).

- Either way, learn how to create and share a [reprex](https://reprex.tidyverse.org/articles/articles/learn-reprex.html) (a minimal, reproducible example), to clearly communicate about your code.

- Check out further details on [contributing guidelines for tidymodels packages](https://www.tidymodels.org/contribute/) and [how to get help](https://www.tidymodels.org/help/).

