---
title: "Fitting and Predicting with poissonreg"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Fitting and Predicting with poissonreg}
output:
  knitr:::html_vignette
---

```{r}
#| label: startup
#| include: false
library(utils)
library(ggplot2)
theme_set(theme_bw())
```

These examples illustrate which models, engines, and prediction types are available in poissonreg. As a reminder, in parsnip, 

- the **model type** differentiates basic modeling approaches, such as random forests, proportional hazards models, etc.,

- the **mode** denotes in what kind of modeling context it will be used (here: regression), and

- the computational **engine** indicates how the model is fit, such as with a specific R package implementation or even methods outside of R like Keras or Stan.

The following examples use the same data set throughout.

## `poisson_reg()` models
  
  <details id="poisson-reg-glm"> 
  
  <summary>With the `"glm"` engine</summary>
  
  ```{r}
  #| echo: false
  knitr::spin_child("template-biochemists.R")
  ```

  We can define the model:
  
  ```{r}
  pr_spec <- 
    poisson_reg() |>
    set_engine("glm") |> 
    set_mode("regression") 
  pr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  pr_fit <- pr_spec |> fit(art ~ ., data = biochemists_train)
  pr_fit
  ```

  The holdout data can be predicted:
  
  ```{r}
  predict(pr_fit, biochemists_test)
  ```
  
  </details>
  
  <details id="poisson-reg-glmnet"> 
  
  <summary>With the `"glmnet"` engine</summary>
  
  ```{r}
  #| echo: false
  knitr::spin_child("template-biochemists.R")
  ```

  We can define the model with specific parameters:
  
  ```{r}
  pr_spec <- 
    poisson_reg(penalty = 0.1) |>
    set_engine("glmnet") |> 
    set_mode("regression") 
  pr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  pr_fit <- pr_spec |> fit(art ~ ., data = biochemists_train)
  pr_fit
  ```

  The holdout data can be predicted:
  
  ```{r}
  predict(pr_fit, biochemists_test)
  ```
  
  </details>

  <details id="poisson-reg-hurdle"> 
  
  <summary>With the `"hurdle"` engine</summary>
  
  ```{r}
  #| echo: false
  knitr::spin_child("template-biochemists.R")
  ```

  We can define the model:
  
  ```{r}
  pr_spec <- 
    poisson_reg() |>
    set_engine("hurdle") |> 
    set_mode("regression") 
  pr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  pr_fit <- pr_spec |> fit(art ~ . | ., data = biochemists_train)
  pr_fit
  ```

  The holdout data can be predicted:
  
  ```{r}
  predict(pr_fit, biochemists_test)
  ```
  
  </details>

  <details id="poisson-reg-stan"> 
  
  <summary>With the `"stan"` engine</summary>
  
  ```{r}
  #| echo: false
  knitr::spin_child("template-biochemists.R")
  ```

  We can define the model:
  
  ```{r}
  pr_spec <- 
    poisson_reg() |>
    set_engine("stan") |> 
    set_mode("regression") 
  pr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  pr_fit <- pr_spec |> fit(art ~ ., data = biochemists_train)
  pr_fit
  ```

  The holdout data can be predicted:
  
  ```{r}
  predict(pr_fit, biochemists_test)
  ```
  
  </details>

  <details id="poisson-reg-zeroinfl"> 
  
  <summary>With the `"zeroinfl"` engine</summary>
  
  ```{r}
  #| echo: false
  knitr::spin_child("template-biochemists.R")
  ```

  We can define the model:
  
  ```{r}
  pr_spec <- 
    poisson_reg() |>
    set_engine("zeroinfl") |> 
    set_mode("regression") 
  pr_spec
  ```

  Now we create the model fit object:
  
  ```{r}
  set.seed(1)
  pr_fit <- pr_spec |> fit(art ~ . | ., data = biochemists_train)
  pr_fit
  ```

  The holdout data can be predicted:
  
  ```{r}
  predict(pr_fit, biochemists_test)
  ```
  
  </details>
